PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 1$

### 2014-07-25 qfenv_paper/qf_environment.tex
edits to SMF section

In order to consistently measure environment throughout our entire sample we impose PRIMUS redshift errors on our SDSS galaxies. However, we observe a significant difference between the SDSS and PRIMUS samples in the fractional contribution of each environment classification within the redshift bin. For each of the PRIMUS redshift bins, approximately $50 \%$ of galaxies in the redshift bin are in low density environments and roughly $30 \%$ are in high density environments. In contrast, in the SDSS redshift bin, $38 \%$ of galaxies in the redshift bin are in low density environments and $45 \%$ are in high density environments. 
As a result, we note that the SMF redshift evolution is inconsistent when transition from the PRIMUS sample to the SDSS sample at $z \sim 0.2$.

Yet, just from the PRIMUS samples alone, we probe a sufficient redshift range to observe certain trends in the SMF evolution for each of the panels in Figure \ref{fig:smf}.

>>>>

In order to consistently measure environment throughout our entire sample we impose PRIMUS redshift errors on our SDSS galaxies. However, we observe a significant difference between the SDSS and PRIMUS samples in the fractional contribution of each environment classification within the redshift bin. For each of the PRIMUS redshift bins, approximately $50 \%$ of galaxies in the redshift bin are in low density environments and roughly $30 \%$ are in high density environments. In contrast, in the SDSS redshift bin, $38 \%$ of galaxies in the redshift bin are in low density environments and $45 \%$ are in high density environments. As a result, we caution that the SMF redshift evolution is inconsistent when transition from the PRIMUS sample to the SDSS sample at $z \sim 0.2$.

Yet, just from the PRIMUS samples alone, we probe a sufficient redshift range to observe notable trends in the SMF evolution for each of the panels in Figure \ref{fig:smf}.
